Data Specialization for a Staged Lambda Calculus

### 2015-02-20 paper/semantics.tex
section 3 - reword the remark about unstaged evaluation

We evaluate \lang\ terms in two stages. The first stage of evaluation:
\begin{enumerate}
\item fully reduces terms in \bbonep, as they are purely first-stage;
\item reduces terms in \bbonem, skipping over any world \bbtwo\ terms they may
contain (inside $\next$);
\item does not reduce terms in \bbtwo, but scans them for any \bbonem\ terms
they may contain (inside $\prev$) and reduces those.
\end{enumerate}
These tasks are accomplished by the $\redsym$, $\redonesym$, and $\redtwosym$
big-step judgments, respectively (all defined in \ref{fig:diaSemantics}).

This process ultimately produces a monostaged term, called a \emph{residual},
all of whose redexes are second-stage computations. The second stage of
evaluation is therefore just ordinary (unstaged) evaluation of this residual,
which we notate $\redsym$. (We assume there is a single notion of unstaged
evaluation applicable to both \bbonep\ terms and residuals. For space reasons,
we omit its definition.)

>>>>

We evaluate \lang\ terms in two stages. The first stage of evaluation:
\begin{enumerate}
\item fully reduces terms in \bbonep, as they are purely first-stage;
\item reduces terms in \bbonem, skipping over any world \bbtwo\ terms they may
contain (inside $\next$);
\item does not reduce terms in \bbtwo, but scans them for any \bbonem\ terms
they may contain (inside $\prev$) and reduces those.
\end{enumerate}
These tasks are accomplished by the $\redsym$, $\redonesym$, and $\redtwosym$
big-step judgments, respectively (defined in \ref{fig:diaSemantics}).

This process ultimately produces a monostaged term, called a \emph{residual}
(\ref{fig:values}), all of whose redexes are second-stage computations. The
second stage of evaluation is therefore just ordinary (unstaged) evaluation of
this residual, which we notate $\redsym$. (For simplicity, we treat residuals
and \bbonep\ terms as living in a single language equipped with a standard
evaluation $\redsym$, whose definition we omit for space reasons.)
